Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-14 doc/Paper/main.tex
Updated some plots and results.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
\caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}
\label{fig:covmat}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\subfigure[$C_{\ell}^{00}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}}
\subfigure[$C_{\ell}^{11}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}} \\
\subfigure[$C_{\ell}^{22}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}}
\subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}} 
\caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} 
\label{fig:covariance-contributions}
\end{center}
\end{figure}

@@

\begin{sidewaystable}
\caption{\todo{UPDATE last 4 entries} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants. The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$. In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$. The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
\begin{center}
\begin{tabular}{ccccccccc}
\hline\hline 
Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
fiducial & $\sfrac{82.0}{80}$ $(0.42)$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $11.89\substack{+0.24 \\ -0.25}$ & $1.49\substack{+3.21 \\ -3.08}$ & $13.09\substack{+0.29 \\ -0.30}$ & - & - & - \\
auto & $\sfrac{18.0}{25}$ $(0.84)$ & $-0.665\substack{2.66 \\ -2.72}$ & $11.78\substack{0.31 \\ -0.28}$ & $0.705\substack{+3.29 \\ -3.30}$ & $12.95\substack{+0.37 \\ -0.33}$  & - & - & - \\
G cov & $\sfrac{83.4}{80}$ $(0.38)$ & $-0.0602\substack{+2.71 \\ -2.16}$ & $11.91\substack{+0.20 \\ -0.21}$ & $1.46\substack{+3.36 \\ -2.78}$ & $13.10\substack{+0.25 \\ -0.26}$ & - & - & - \\
G+SSC cov & $\sfrac{83.0}{80}$ $(0.39)$ & $-0.370\substack{+2.38 \\ -2.18}$ & $11.87\substack{+0.24 \\ -0.25}$ & $1.12\substack{+3.05 \\ -2.75}$ & $13.06\substack{+0.29 \\ -0.30}$ & - & - & - \\
no $z_{w, i}$ & $\sfrac{83.6}{84}$ $(0.49)$ & $0.770\substack{+0.679 \\ -0.891}$ & $11.86\substack{+0.13 \\ -0.14}$ & $0.494\substack{+0.929 \\ -1.21}$ & $13.05\substack{+0.18 \\ -0.20}$ & - & - & - \\
no $z_{w, i}, \Delta z_{i}$ & $\sfrac{90.2}{88}$ $(0.42)$ & $-1.16\substack{+0.632 \\ -0.845}$ & $11.75 \pm 0.14$ & $-0.130\substack{+0.687 \\ -1.01}$ & $12.89 \pm 0.17$ & - & - & - \\
bins = 0, 1, 2 & $\sfrac{41.0}{43}$ $(0.56)$ & $-0.408\substack{+2.35 \\ -2.46}$ & $11.84 \pm 0.25$ & $0.585\substack{+2.84 \\ -2.99}$ & $13.03\substack{+0.31 \\ -0.30}$ & - & - & - \\
bins = 1, 2, 3 & $\sfrac{42.6}{46}$ $(0.62)$ & $1.22\substack{+3.27 \\ -3.22}$ & $11.94\substack{+0.34 \\ -0.39}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
pz = \texttt{Ephor\_AB} & $\sfrac{89.6}{80}$ $(0.22)$ & $0.396\substack{+2.2 \\ -2.1}$ & $12.12\substack{+0.20 \\ -0.19}$ & $2.02\substack{+3.07 \\ -2.88}$ & $13.37\substack{+0.27 \\ -0.26}$ & - & - & - \\
pz = \texttt{Ephor} & $\sfrac{102.0}{80}$ $(0.049)$ & $1.16\substack{+2.02 \\ -2.09}$ & $12.14\substack{+0.18 \\ -0.17}$ & $3.01\substack{+2.75 \\ -2.87}$ & $13.39\substack{+0.23 \\ -0.22}$ & - & - & - \\
pz = \texttt{DEmP} & $\sfrac{100.8}{80}$ $(0.058)$ & $0.493\substack{+1.93 \\ -1.97}$ & $12.03 \pm 0.20$ & $2.15\substack{+2.64 \\ -2.67}$ & $13.25 \pm 0.27$ & - & - & - \\
pz = \texttt{FRANKEN-Z} & $\sfrac{87.2}{80}$ $(0.27)$ & $0.387\substack{+1.99 \\ -1.96}$ & $12.13 \pm 0.18$ & $2.00\substack{+2.79 \\ -2.74}$ & $13.38 \pm 0.24$ & - & - & - \\
fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
fit magn., auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.16\substack{+1.80 \\ -1.63}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.34\substack{+2.52 \\ -2.29}$ & $13.72\substack{+0.20 \\ -0.19}$  & $-0.25\substack{+1.34 \\ -1.27}$ & - & - \\
fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
 \hline \hline
\end{tabular}
\end{center}
\end{sidewaystable}

As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross power spectra. However, cross correlations between redshift bins are susceptible to photometric redshift errors, such as outliers. In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross power spectra. Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto power spectra alone. As can be seen, the constraints from auto power spectra and auto- and cross power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis. Furthermore, we see that the constraining power on HOD parameters is unaffected by including the cross power spectra. As a final consistency check between auto- and cross power spectra we test how well the auto power spectra predict the cross power spectra. To this end we compute the $\chi^{2}$ between the observed auto- and cross power spectra and the theoretical predictions derived from auto power spectra only. As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test. We find $\chi^{2} = 90.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}). This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
\caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}
\label{fig:covmat}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\subfigure[$C_{\ell}^{00}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}}
\subfigure[$C_{\ell}^{11}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}} \\
\subfigure[$C_{\ell}^{22}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}}
\subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}} 
\caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} 
\label{fig:covariance-contributions}
\end{center}
\end{figure}

@@

\begin{sidewaystable}
\caption{\todo{UPDATE last 4 entries} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants. The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$. In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$. The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
\begin{center}
\begin{tabular}{ccccccccc}
\hline\hline 
Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
fiducial & $\sfrac{82.0}{80}$ $(0.42)$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $11.89\substack{+0.24 \\ -0.25}$ & $1.49\substack{+3.21 \\ -3.08}$ & $13.09\substack{+0.29 \\ -0.30}$ & - & - & - \\
auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $13.00 \pm 0.33$  & - & - & - \\
G cov & $\sfrac{80.6}{80}$ $(0.46)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.433\substack{+1.96 \\ -1.90}$ & $11.89 \pm 0.20$ & $0.982\substack{+2.55 \\ -2.44}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\
no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.855\substack{+0.645 \\ -0.652}$ & $11.87 \pm 0.11$ & $0.327\substack{+0.889 \\ -0.900}$ & $13.07 \pm 0.15$ & - & - & - \\
no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.624 \\ -0.771}$ & $11.78 \pm 0.13$ & $-0.108\substack{+0.727 \\ -0.940}$ & $12.93 \pm 0.16$ & - & - & - \\
bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.354\substack{+2.34 \\ -2.25}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.624\substack{+2.87 \\ -2.75}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.20\substack{+2.88 \\ -2.97}$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.270\substack{+2.05 \\ -1.88}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.82\substack{+2.87 \\ -2.59}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\
pz = \texttt{Ephor} & $\sfrac{107.2}{80}$ $(0.023)$ & $0.895\substack{+1.97 \\ -2.03}$ & $12.15 \pm 0.17$ & $2.64\substack{+2.71 \\ -2.80}$ & $13.40\substack{+0.23 \\ -0.22}$ & - & - & - \\
pz = \texttt{DEmP} & $\sfrac{105.4}{80}$ $(0.031)$ & $0.616\substack{+1.90 \\ -1.88}$ & $12.07\substack{+0.17 \\ -0.16}$ & $2.29\substack{+2.59 \\ -2.55}$ & $13.30\substack{+0.22 \\ -0.21}$ & - & - & - \\
pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0421\substack{+1.97 \\ -1.76}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.41\substack{+2.75 \\ -2.44}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\
fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
 \hline \hline
\end{tabular}
\end{center}
\end{sidewaystable}

As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross power spectra. However, cross correlations between redshift bins are susceptible to photometric redshift errors, such as outliers. In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross power spectra. Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto power spectra alone. As can be seen, the constraints from auto power spectra and auto- and cross power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis. Furthermore, we see that the constraining power on HOD parameters is unaffected by including the cross power spectra. As a final consistency check between auto- and cross power spectra we test how well the auto power spectra predict the cross power spectra. To this end we compute the $\chi^{2}$ between the observed auto- and cross power spectra and the theoretical predictions derived from auto power spectra only. As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test. We find $\chi^{2} = 95.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}). This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.
